The limits of self commitment and private paternalism \thanks{}

### 2022-01-29 donde.tex
update tex file

We now develop the measures of net financial costs to the borrower that are used as our core pecuniary outcomes.  The two key measures are loan default, and the effective financial cost incurred by the borrower. Default is defined as losing the pawn. Let $P^c$, $P^f$, and $P^i$ the payments to principal, fees, and interest respectively. We define financial cost as the discounted sum of payments toward the loan, plus the discounted payment of fees, plus payments to interest, plus the appraised value of the pawn, and subtract the appraised value of the pawn when it is recovered: 
\begin{align*}
    Financial \; Cost_i =& \underbrace{\sum_t \frac{P^c_{it}}{(1+r)^t}}_{\text{Discounted payments to capital}} + \underbrace{\sum_t \frac{P^f_{it}}{(1+r)^t}}_{\text{Payed fees}}  +\underbrace{\sum_t \frac{P^i_{it}}{(1+r)^t}}_{\text{Payed interests}} \\
    &\quad\qquad + \underbrace{Pawn \: Value_i - \frac{\text{I}(Recovered \: Pawn_i) \times Pawn \: Value_i}{(1+r)^T}}_{\text{Cost of losing pawn}}
\end{align*}

@@

@@

%\textit{Do file: } \texttt{ss.do}
\end{table}

@@

\begin{figure}[H]
     \caption{Experiment description}
    \label{exp_description}
    \begin{center}
    \begin{subfigure}{.40\textwidth}
      \caption{Timeline of the experiment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/timeline_suc_exp_extended.pdf}
    \end{subfigure}
    \begin{subfigure}{0.40\textwidth}
    \caption{Experiment arms}
       \centering
      \includegraphics[width=\textwidth]{Figuras/exp_arms.PNG}
    \end{subfigure}
    \end{center}
         \scriptsize Panel (a) displays in black arrows the period covered by our administrative data: from August 6th 2012 (30 days before the experiment began : pre-experiment period) to August 13th 2013. The gray lines correspond to the dates of implementation of the experiment. We finished the experiment earlier in branches 1 and 2 because we realized that we would have enough sample size with the remaining branches and wanted to save on operational costs. Panel (b) shows our 5 treatment arms: control (status quo contract), no Forced Commitment, promise-forcing, choice among status quo and fee-commitment, and choice among status quo Soft Commitment. Within each arm it displays the number of observations. For the choice groups it splits the sample size into those who chose the commitment contract (shaded blue triangle) and those that did not (un-shaded triangle).
%\textit{Do file: }  \texttt{timeline\_suc\_exp.do}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% APPENDIX 
\setcounter{table}{0}
\setcounter{figure}{0}
\setcounter{section}{0}
\pagenumbering{gobble}

\begin{center}
	\LARGE The limits of self-commitment and private paternalism \\[0.5em]
	\Large{Appendix $-$ For Online Publication} \\[1em]
	\large \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira}
\end{center}

\appendix
\pagenumbering{arabic}
\renewcommand\thefigure{OA-\arabic{figure}}
\renewcommand\thetable{OA-\arabic{table}}
\renewcommand*{\thepage}{OA - \arabic{page}}
\renewcommand\thesection{Appendix \Alph{section}.}
\renewcommand\thesubsection{\Alph{section}.\arabic{subsection}}

%\renewcommand{\cftparskip}{0em} % NOT NEEDED
\renewcommand\cftsecdotsep{\cftdotsep}
\renewcommand\cftsubsecdotsep{\cftnodots}
\renewcommand{\cftsecnumwidth}{6em}
 \renewcommand{\cftpnumalign}{r}
%\renewcommand{\cftsecleader}{\normalfont\cftdotfill{\cftsecdotsep}}

\renewcommand{\cftsecleader}{\cftdotfill{\cftsecdotsep}\hspace{1.8em}}
%\renewcommand{\cftsecpagefont}{20em}
%\renewcommand{\cftfignumwidth}{6em}
%\renewcommand{\cfttabnumwidth}{3.3em}

%\tableofcontents
\etocdepthtag.toc{mtappendix}
\etocsettagdepth{mtchapter}{none}
\etocsettagdepth{mtappendix}{subsection}

\setstretch{0.9}
%\renewcommand\contentsname{} % the empty name

\begingroup
\let\clearpage\relax
%\vspace{-1.5em} % the removed space. Set as appropriate
\tableofcontents
\endgroup

\section{ Further results}
\vspace{.2in}

\subsection{Some materials}

\vspace{.1in}
\begin{figure}[H]
     \caption{Contract Terms Summary, and Promise Slip}
    \label{PaperSlip}
    \begin{center}
    \begin{subfigure}{0.65\textwidth}
    \caption{Receipt for client}
        \centering
        \includegraphics[width=\textwidth]{Figuras/TicketLenderP.png}
    \end{subfigure}

    \vspace{3ex}
    \begin{subfigure}{0.65\textwidth}
    \caption{Personal promise signed by client}
        \centering
        \includegraphics[width=\textwidth]{Figuras/Personal Promise2.png}
    \end{subfigure}
    \end{center}
    \scriptsize
        The top of this figure is a sample receipt that was given to clients that got assigned to the Forced Commitment contract (the font and format were changed to protect Lender's P identity). We want to highlight the salience of some items. First the title clearly indicated which contract the client has (arrow 1). Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 4\% of the value of the monthly payment (arrow 2). Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month. The bottom panel of the figure shows a ``promise slip'', the paper that those who were assigned (or chose) to the monthly payment with promise had to sign to make the promise salient. It emphasizes that the client is giving his word, and that the promise is not a legal document.
\end{figure}

\subsection{Pictures}

\begin{figure}[H]
     \caption{Some Pawnshops}
    \label{PawnshopPicture}
    \begin{center}
    \begin{subfigure}{0.42\textwidth}
    \caption{Appraiser/tellers inside a pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio9.png}
    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
    \caption{Pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio11.png}
    \end{subfigure}

    \begin{subfigure}{0.45\textwidth}
    \caption{Pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio2.png}
    \end{subfigure}
    \begin{subfigure}{0.42\textwidth}
    \caption{Lost pawns which are for sale}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio3.png}
    \end{subfigure}

    \end{center}
    \scriptsize
        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
\end{figure}

\vspace{.1in}
\begin{figure}[H]
     \caption{Gold buyers next to pawnshops}
    \label{GoldBuyers}
    \begin{center}
    \begin{subfigure}{.49\textwidth}
    \caption{Gold buyer next to pawnshop 1}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio7.png}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
    \caption{Gold buyer next to pawnshop 1}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio8.png}
    \end{subfigure}
       \vspace{3ex}

    \end{center}
    \scriptsize
        This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
\end{figure}

%\begin{figure}[H]
%        \caption{Booklet with product information}
%    \label{micas}
%    \begin{center}
%        \centering
%        \includegraphics[width=\textwidth]{micas.pdf}
%    \end{center}
%     \footnotesize \textit{Notes: } 
%      \footnotesize{ }
%\end{figure}

%\begin{figure}[H]
%     \caption{Booklet with product information translated}
%    \label{booklet_translate2}
%    \begin{center}
%    \begin{subfigure}{.9\textwidth}
%        \centering
%        \includegraphics[width=\textwidth]{Figuras/MP_F.pdf}
%    \end{subfigure}
    %\begin{subfigure}{0.55\textwidth}
    %   \centering
    %  \includegraphics[width=\textwidth]{Figuras/MP_2.pdf}
    %\end{subfigure}
%    \end{center}
%\end{figure}

\subsection{Surveys}

\begin{table}[H]
\caption{Survey's non-response balance}
\label{balance_response}
\begin{center}
\scriptsize{\input{./Tables/balance_response.tex}}
\end{center}
 \scriptsize This table shows whether the means of variables in the administrative dataset are different for those that respond the baseline survey vs those that do not. We use this as an assessment of external validity. Internal validity is guaranteed because the baseline survey was implemented before treatment assignment and therefore response rates are orthogonal to treatment assignments. Panel A studies the baseline survey, while Panel B focuses on the exit survey. The columns labeled ``p-values'' report p-values for the test that the means of the respective variable are the same for those that responded did not respond the survey.
%\textit{Do file: } \texttt{balance\_response.do}
\end{table}

\afterpage{
\begin{table}[H]
\caption{Baseline survey}
\label{baseline_survey}
\begin{center}
\scriptsize{\input{./Tables/transcribed.tex}}
\end{center}
\end{table}
}

\begin{comment}
\begin{table}[H]
\caption{Reincidence SS}
\label{tab_reincidence}
\begin{center}
\scriptsize{\input{./Tables/tab_reincidence.tex}}
\end{center}
 \scriptsize
%\textit{Do file: } \texttt{tab\_reincidence.do}
\end{table}

\begin{table}[H]
\caption{Summary statistics (exit survey)}
\label{SS_exit}
\begin{center}
\scriptsize{\input{./Tables/SS_exit.tex}}
\end{center}
 \scriptsize We carried out an exit survey. It had a small response rate and we don't use it in the paper. Here it shows that the characteristics of those that responded it are balanced across arms (Panel B). Panel A reports outcomes.
%\textit{Do file: } \texttt{ss.do}
\end{table}
\end{comment}

\newpage
\subsection{Some more evidence of overconfidence}

\vspace{.2in}
\begin{figure}[H]
    \caption{Behavior of those who lost pawn}
    \label{proxy_naive}
    \begin{center}
    \begin{subfigure}{0.40\textwidth}
        \caption{Elapsed days to first payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
    \end{subfigure}
    \begin{subfigure}{0.40\textwidth}
        \caption{Elapsed days to last payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
    \end{subfigure}
        \begin{subfigure}{0.40\textwidth}
        \caption{Payments as \% of loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
    \end{subfigure}
    \begin{subfigure}{0.40\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
    \end{subfigure}
    \end{center}
        \scriptsize 
        This figure describes behavior for the subsample of clients whose pawn was not recovered (in the control group).  Panel (a) shows days elapsed from the pawn to the first payment, while panel (b) displays the days elapsed to last payment. Some people pay after the day 105 when the grace period ends because the can ``restart'' the loan if they pay all interest owed. It amounts to starting a new loan with the same conditions and same pawn. Panel (c) shows the fraction of the loan that they paid (even when they ended up losing the pawn). Panel (d) displays the number of times they went to the branch to pay.      
      %\textit{Do file: }  \texttt{hist\_den\_default.do}
\end{figure}

\newpage
\subsection{Main treatment effects: Additional material}

\vspace{.2in}

\begin{figure}[H]
        \caption{FC conditional on first 115 days - treatment effect}
    \label{fc_pro_2_115}
    \begin{center}
        \centering
        \includegraphics[width=0.50\textwidth]{Figuras/fc_te_115_pro_2.pdf}
    \end{center}
     \scriptsize This figure is the same as in Figure \ref{fc_pro2} Panel (a), but with the subsample restricted to the first 115 days.
     %\textit{Do file: }  \texttt{fc\_te\_115.do}
\end{figure}

\begin{figure}[H]
        \caption{Financial cost effect: charging all fees}
    \label{fc_allfee}
    \begin{center}
        \centering
        \includegraphics[width=0.50\textwidth]{Figuras/fc_allfee_quantile_pro_2.pdf}
    \end{center}
    \scriptsize
     This figure is the analogous to Figure \ref{fc_pro2}(b), except that for the Forced Commitment contract we pretend that all clients incurred in their late fees, and therefore inflate the financial cost by summing those fees. This is intended as a kind of worse case scenario for the financial cost of the Forced Commitment contract. The circles indicate the quantile treatment effects, while the cross is the (OLS) mean. We still find that the financial cost of will be smaller under the Forced Commitment contract in spite of artificially inflating it.
     %\texttt{fc\_all\_fee.do}
\end{figure}

\begin{figure}[H]
        \caption{FC as \% of loan - treatment effect}
    \label{fc_perc}
    \begin{center}
        \centering
        \includegraphics[width=0.50\textwidth]{Figuras/fc_perc_te_allarms.pdf}
    \end{center}
     \scriptsize This figure shows the estimated treatment effect of all arms against the status quo, but normalizing the dependent variable by the value of the loan.
     %\textit{Do file: }  \texttt{fc\_perc\_allarms.do}
\end{figure}

\begin{figure}[H]
    \caption{Relationship between treatment effects}
    \label{induced_to_pay_early}
    \begin{center}
    \begin{subfigure}{0.45\textwidth}
        \caption{\footnotesize{Induced to pay earlier vs Induced Lower FC}}
        \centering
        \includegraphics[width=\textwidth]{Figuras/binscatter_fc_days_pro_2.pdf}
    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \caption{\footnotesize{Induced to pay earlier vs Induced Recovery}}
        \centering
        \includegraphics[width=\textwidth]{Figuras/binscatter_def_days_pro_2.pdf}
    \end{subfigure}
    \end{center}
       \scriptsize 
       This figure plots relationships between \textit{treatment effects}. Both Panels (a) an (b) have the same X-axis, which displays the estimated heterogeneous treatment effect on the outcome ``elapsed days of first payment'', that is how many days elapsed from the day the loan was awarded to the first payment the client made. The treatments effects were calculated using \cite{atheygrf}. In Panel (a) the Y-axis is the \textit{treatment effect} on financial cost. In Panel (b) the Y-axis is the \textit{treatment effect} on losing their pawn. Panel (a) shows that those induced to pay earlier are also those that have larger savings in financial cost as a result of ``forcing'' the frequent payment commitment contract compared to the status-quo (control). Panel (b) shows that those induced to pay earlier are also those that have a larger increase in recovery.
      %\textit{Do file: }  \texttt{binscatter\_hte.do}
\end{figure}

\begin{figure}[H]
        \caption{Repeat purchase before 30/60 days}
    \label{reincidence_before}
    \begin{center}
        \centering
        \includegraphics[width=0.50\textwidth]{Figuras/re_te_earlydays.pdf}
    \end{center}
     \scriptsize This figure shows the estimated treatment effect of repeat purchase before 30 \& 60 days.
     %\textit{Do file: }  \texttt{re\_te\_earlydays.do}
\end{figure}

\begin{table}[H]
\caption{Intermediate outcomes}
\label{mechanisms}
\begin{center}
\scriptsize{\input{./Tables/mechanism.tex}}
\end{center}

%\textit{Do file: } \texttt{mechanisms.do}
\end{table}

\scriptsize {
\noindent This table explores treatment effects in ``intermediate variables''. Each column represents a different dependent variable in an OLS regression, and each panel represents a different treatment arm-control comparison. All regressions include fixed effects for branch, day of week fixed effects, number of pawns at the time of pawning this particular one, number of different treatment arms experienced before pawning this particular one. $R^2$ are not reported, they were less than 0.04 for all but the last column which had $R^2$'s close to 0.6. The last row shows the mean of the dependent variable for the control group. Dependent variables are as follows: Column (1) measures the number of days elapsed from the pawning date to the first payment done. Column (2) records the number of payments done within 230 days of the pawn. Column (3) is the average size of the payments for each client in pesos. Column (4) is self-reported cost to get to the branch plus the imputed loss of a whole day of salary (using the minimum wage in Mexico) multiplied by the number of visits to the branch. Column (5) measures the number of days it took to recover the pawn, conditional on recovering. The dependent variable in Column (6) is a dummy =1 if the client paid any positive amount within 230 days of the pawn. For Columns (7) and (8) the dependent variable it is the sum of total payments done within 230 days of the pawn divided by the size of the loan, but column (8) includes as regressors a dummy=1 if the client recovered her pawn, and its interaction with treatment.
}

\subsection{FOSD: fee forcing vs status quo financial cost distributions}

\vspace{.2in}
\begin{figure}[H]
        \caption{Empirical CDF of Financial Cost: fee-focing vs status-quo}
    \label{ecdf_fc}
    \begin{center}
        \centering
        \includegraphics[width=0.65\textwidth]{Figuras/cdf_fc_pro_2.pdf}
    \end{center}
    \scriptsize This figure plots the empirical cumulative distribution of financial cost. It does this separately for the Forced Commitment contract and for the status-quo contract. The doted line at the bottom is the difference of the status-quo CDF minus the fee-focing CDF. It shows that the CDF of the status quo contract is always below that of the Forced Commitment (and this difference is significant for the points indicated by the blue line), and therefore that the former first-order stochastically dominates the later for weakly decreasing utility functions; see Proposition \ref{eq_fosd}.
    % \texttt{ecdf\_fc.do}}
\end{figure}

\vspace{.2in}
\begin{table}[H]
\caption{Clients who should prefer Forced Commitment financial cost distribution}
\label{stochastic_dominance}
\begin{center}
\scriptsize{\input{./Tables/dominance.tex}}
\end{center}
 \scriptsize
This table does two things. First, it tests whether the observed empirical distribution of financial cost is well approximated by a log normal. It does this using two tests, the Anderson-Darling and the Kolmogorov-Smirnoff tests. Second, it fits a log normal distribution by maximum likelihood to observed empirical distribution of financial cost, separately for the Forced Commitment arm and the status-quo arm. Using the fitted log normal, it tests whether the Forced Commitment financial cost distribution would be preferred by any expected utility agent using Proposition \ref{lognormal_fosd} below. The different rows of the table do this for different sub-populations.  The first row of the table does it for every client in the fee forcing and status quo arms. The ``*'' show that we cannot reject at the 5\% level that both distribution are log normal for any of the two tests. The column entitled ``Dominance'' shows whether any client that dislikes higher cost would prefer the Forced Commitment cost distribution over the status quo one, with $\succeq_{1}$ meaning he should (with $\succeq_{1}^*$ indicating the difference is statistically significant). It turns out to be the case that for the overwhelming majority of sub-populations, the conditions of preferring the Forced Commitment distribution hold.
%\textit{Do file: } \texttt{stoch\_dominance.do}
\end{table}

\vspace{.2in}
\begin{prop}
\label{lognormal_fosd}
\footnotesize{
Let $F$ and $G$ be the cumulative distributions of two alternative log-normal prospects. The following are equivalent:

\begin{enumerate}[(a)]
    \item For every weakly decreasing utility function $u$: $E_{F}(u(FC))\leq E_G(u(FC))$
    \item $E_F \log(FC)\geq E_G\log(FC)$ and $Var_F \log(FC)= Var_G\log(FC)$
\end{enumerate}
}
\end{prop}

\begin{proof}
\footnotesize{
See Theorem 4 in \cite{lognormal_dominance}.
}
\end{proof}

\vspace{.1in}
\begin{prop}
\label{eq_fosd}
\footnotesize{
This is a standard result. 
\\
\vspace{.1in}
The following are equivalent:
\begin{enumerate}[(a)]
    \item For every weakly decreasing utility function $u$: $E_{sq}(u(FC))\leq E_{fee}(u(FC))$
    \item $F_{sq}(FC)\leq F_{fee}(FC)$ 
\end{enumerate}
}
\end{prop}
\begin{proof} \;
\footnotesize{

[$(a)\Longrightarrow (b)$] Suppose  $(b)$ does not hold. So there exists $FC^*$ such that $F_{sq}(FC^*)>F_{fee}(FC^*)$, Define $u:=\mathds{1}_{FC\leq FC^*}$. Then
\[E_{sq}(u(FC)) = \int u(FC)dF_{sq} = F_{sq}(FC^*)>F_{fee}(FC^*)= \int u(FC)dF_{fee} =E_{fee}(u(FC))\]
which contradicts $(a)$.\\

[$(a)\Longleftarrow (b)$] On the other hand for $u$ weakly decreasing,

\[\int u(y(FC))dF_{sq}(y(FC)) = \int u(y(FC))dF_{fee}(FC) \leq \int u(FC)dF_{fee}(FC)\]
with $y(FC) = F_{sq}^{-1}F_{fee}(FC)$.
}
\end{proof}
\footnotesize{
Note the proof was done in the case of absolutely continuous and strictly increasing distribution functions $F_{sq}$ and $F_{fee}$.
}

\newpage
\subsection{Causal Random Forest and HTE}

\vspace{.3in}
\begin{figure}[H]
        \caption{Honest causal tree for the fee forcing contract heterogenous treatment effects}
    \label{casual_tree}
    \begin{center}
        \centering
        \includegraphics[width=.8\textwidth]{Figuras/crf_pro_2_fc_admin_disc.pdf}
    \end{center}
    \footnotesize 
    This is one(it is chosen such that it minimizes the pruned cost, that is it is the tree with the smallest root-node impurity) of the honest causal trees in the random forest we use for the estimation of the heterogeneous treatment effect of the Forced Commitment contract. It is meant only as an example of how these trees look like. The forest was such that there are as many estimated treatment effects as there are clients.
     %\footnotesize{ \textit{RScript: }  \texttt{grf.R}
\end{figure}

We use \cite{atheygrf} \texttt{causal\_forest} of the \texttt{grf} library in $R$. The parameters used were:
\scriptsize{\textit{causal\_forest(
  X, 
  Y, 
  W, 
  Y.hat = NULL, 
  W.hat = NULL, 
  num.trees = 2000, 
  sample.weights = NULL, 
  clusters = NULL, 
  equalize.cluster.weights = FALSE, 
  sample.fraction = 0.5, 
  mtry = min(ceiling(sqrt(ncol(X)) + 20),ncol(X)), 
  min.node.size = 5, 
  honesty = TRUE, 
  honesty.fraction = 0.5, 
  honesty.prune.leaves = TRUE, 
  alpha = 0.05, 
  imbalance.penalty = 0, 
  stabilize.splits = TRUE, 
  ci.group.size = 2, 
  tune.parameters = "none", 
  tune.num.trees = 200, 
  tune.num.reps = 50, 
  tune.num.draws = 1000, 
  compute.oob.predictions = TRUE, 
  orthog.boosting = FALSE, 
  num.threads = NULL)}}

\begin{figure}[H]
    \caption{Heterogeneous Treatment Effect: Forced Commitment contract}
    \label{HTE_fee_forcing}
    \begin{center}
    %\begin{subfigure}{0.4\textwidth}
    %    \caption{Financial cost}
    %    \centering
    %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
    %\end{subfigure}
    \begin{subfigure}{0.7\textwidth}
        \caption{Determinants of effects}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_2.pdf}
    \end{subfigure}

    %\begin{subfigure}{0.4\textwidth}
    %    \caption{Losing Pawn}
    %    \centering
    %    \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
    %\end{subfigure}
    %\begin{subfigure}{0.4\textwidth}
    %    \caption*{}
    %    \centering
    %    \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_2.pdf}
    %\end{subfigure}
    \end{center}
     \scriptsize  This figure estimates bivariate regressions of the estimated client-level heterogeneous treatment effects against the respective covariate from the baseline survey  $\widehat{hte_i} = \alpha + \beta \: X_i + \epsilon_i$. The regressors $X_i$ include (e.g if the family asks for money, if they have savings, if they are overconfident using the definition the text, etc. See this Appendix for a transcription of the survey).
      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
\end{figure}

\begin{comment}
\begin{figure}[H]
    \caption{Heterogeneous Treatment Effect: Promise-forcing contract}
    \label{heterogeneous_te_3}
    \begin{center}
    \begin{subfigure}{0.4\textwidth}
        \caption{Financial cost}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_3.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption*{}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_3.pdf}
    \end{subfigure}

    \begin{subfigure}{0.4\textwidth}
        \caption{Losing Pawn}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_3.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption*{}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_3.pdf}
    \end{subfigure}
    \end{center}
     \scriptsize
      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
\end{figure}
\end{comment}

\begin{comment}

\begin{figure}[H]
    \caption{Heterogeneous Treatment Effect - Choice/Fee}
    \label{heterogeneous_te_4}
    \begin{center}
    \begin{subfigure}{0.4\textwidth}
        \caption{Financial cost}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_4.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption*{}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_4.pdf}
    \end{subfigure}

    \begin{subfigure}{0.4\textwidth}
        \caption{Losing Pawn}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_4.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption*{}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_4.pdf}
    \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: } The distribution plots the FC treatment effect for the interval $[\mu-2\sigma,\mu+2\sigma]$ to ignore the outliers.
      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
\end{figure}

\begin{figure}[H]
    \caption{Heterogeneous Treatment Effect - Choice/Promise}
    \label{heterogeneous_te_5}
    \begin{center}
    \begin{subfigure}{0.4\textwidth}
        \caption{Financial cost}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_5.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption*{}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_5.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption{Losing Pawn}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_5.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption*{}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_5.pdf}
    \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
\end{figure}

\end{comment}

%\begin{figure}[H]
%    \caption{Heterogeneous Treatment Effect (FC survey) - All arms}
%    \label{heterogeneous_te_fcsurvey_all}
%    \begin{center}
%    \begin{subfigure}{0.4\textwidth}
%        \caption{Forcing/Fee}
%        \centering
%        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_survey_disc_pro_2.pdf}
%    \end{subfigure}
%    \begin{subfigure}{0.4\textwidth}
%        \caption{Forcing/Promise}
%        \centering
%        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_survey_disc_pro_3.pdf}
%    \end{subfigure}

%    \begin{subfigure}{0.4\textwidth}
%        \caption{Choice/Fee}
%        \centering
%        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_survey_disc_pro_4.pdf}
%    \end{subfigure}
%    \begin{subfigure}{0.4\textwidth}
%        \caption{Choice/Promise}
%        \centering
%        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_survey_disc_pro_5.pdf}
%    \end{subfigure}
%    \end{center}
%     \footnotesize \textit{Notes: } 
%      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
%\end{figure}

\subsection{Take up}

\begin{table}[H]
    \caption{Predicting Take-up: Goodness-of-Fit}
    \label{Table_compliance}
    %\begin{subtable}{1\textwidth}
    % \centering
    %    \caption{Take up}
    %    \scriptsize{\input{./Tables/oos_pago_frec_vol.tex}}
    %\end{subtable}%

    %\bigskip
     \begin{subtable}{1\textwidth}
      \centering
        \caption{Take up: Choice-fee Arm}
        \scriptsize{\input{./Tables/oos_pago_frec_vol_fee.tex}}
    \end{subtable}

      \bigskip
    \begin{subtable}{1\textwidth}
      \centering
        \caption{Take up: Choice-promise Arm}
        \scriptsize{\input{./Tables/oos_pago_frec_vol_promise.tex}}
    \end{subtable}
            \scriptsize
           \\
           \\
           \\

     %\textit{Scripts: } \texttt{pred\_take\_up.do, pfv\_pred.R}
\end{table}

\vspace{.1in}
\begin{figure}[H]
    \caption{Out of sample ROC curve}
    \label{roc_curve}
    \begin{center}
    \begin{subfigure}{0.45\textwidth}
        \caption{Take-up in Fee Arm}
        \centering
        \includegraphics[width=\textwidth]{Figuras/Boost/ROC_curve_outsample_pago_frec_vol_fee.pdf}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \caption{Take-up in Promise Arm}
        \centering
        \includegraphics[width=\textwidth]{Figuras/Boost/ROC_curve_outsample_pago_frec_vol_promise.pdf}
    \end{subfigure}
    \end{center}
     \scriptsize 
  %\footnotesize{ \textit{Do file: }  \texttt{pred\_take\_up.do}}
\end{figure}

\begin{figure}[H]
    \caption{Predictors of commitment contract take-up}
    \label{interactions_takeup}
    \begin{center}
    \begin{subfigure}{0.45\textwidth}
        \caption{with Fee Arm}
        \centering
        \includegraphics[width=\textwidth]{Figuras/pago_frec_vol_fee_interactions_rf.pdf}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \caption{with Promise Arm}
        \centering
        \includegraphics[width=\textwidth]{Figuras/pago_frec_vol_promise_interactions_rf.pdf}
    \end{subfigure}
    \end{center}
     \scriptsize
      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_fvp.do}}
\end{figure}

\scriptsize {
\noindent This figure reports bivariate regressions of the form $\widehat{TakeUp} = \alpha + \beta \: X_i + \epsilon_i$, where $\widehat{TakeUp}$ is the prediction using random forests. The figure reports the $\beta$ coefficients for different $X_i$'s along with 95\% confidence intervals. Panel (a) focuses on take up in the arm where clients could chose among the fee-commitment contract and the status quo contract. Panel (b) focuses on the arm where clients could chose among the Soft Commitment contract and the status quo contract. Using random forests we can predict who takes up the Forced Commitment contract with 85\% accuracy out of sample.\footnote{Correcting for the fact that most chose the status-quo contract using the method of SMOTE, \cite{smote} we find an accuracy rate of 75\%.} Which suggests that choice among contracts is not purely random. This figure shows that the more educated, those that report that their family typically asks for money, those that make a monthly budget of expenses, and those that ask for a remainder of their due payments (and marginally those we classify as present-biased) are more likely to chose the fee-commitment contract if given the choice. The opposite holds for clients that are more economically vulnerable (can barely pay for food, electricity, etc) and those that report being more stressed.
}

%---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------

\subsection{New results}

\begin{table}[H]
\caption{Summary statistics and Balance}
\label{SS}
\begin{center}
\scriptsize{\input{./Tables/SS_appendix.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{SS\_appendix.do}
\end{table}

>>>>

We now develop the measures of net financial costs to the borrower that are used as our core pecuniary outcomes.  The two key measures are loan default, and the effective financial cost incurred by the borrower. Default is defined as losing the pawn. Let $P^c$, $P^f$, and $P^i$ the payments to principal, fees, and interest respectively. We define financial cost as the discounted sum of payments toward the loan, plus the discounted payment of fees, plus payments to interest, plus the appraised value of the pawn, and subtract the appraised value of the pawn when it is recovered: 
\begin{align*}
    Financial \; Cost_i =& \underbrace{\sum_t P^c_{it}}_{\text{Discounted payments to capital}} + \underbrace{\sum_t P^f_{it}}_{\text{Payed fees}}  +\underbrace{\sum_t P^i_{it}}_{\text{Payed interests}} \\
    &\quad\qquad + \underbrace{Pawn \: Value_i - \text{I}(Recovered \: Pawn_i) \times Pawn \: Value_i}_{\text{Cost of losing pawn}}
\end{align*}

@@

\begin{table}[H]
\caption{Attrition table}
\label{attrition_table}
\begin{center}
\scriptsize{\input{./Tables/Attrition.tex}}
\end{center}
 \scriptsize 
%\textit{Do file: } \texttt{ss\_att.do}
\end{table}

@@

%\textit{Do file: } \texttt{ss\_att.do}
\end{table}

@@

\begin{figure}[H]
     \caption{Experiment description}
    \label{exp_description}
\begin{center}
  \begin{minipage}[b]{1.0\linewidth}
    \subcaption{Timeline of the experiment}
    \centering
        \includegraphics[width=0.4\textwidth]{Figuras/timeline_suc_exp_extended.pdf}
        \subcaption{Experiment arms}
\centering        
\scriptsize{\input{./Tables/exp_arms.tex}}
  \end{minipage}
  \end{center}
    \scriptsize Panel (a) displays in black arrows the period covered by our administrative data: from August 6th 2012 (30 days before the experiment began : pre-experiment period) to August 13th 2013. The gray lines correspond to the dates of implementation of the experiment. We finished the experiment earlier in branches 1 and 2 because we realized that we would have enough sample size with the remaining branches and wanted to save on operational costs. Panel (b) shows our 5 treatment arms. It shows the number of observations in each arm together with the observations for the surveys.
%\textit{Do file: }  \texttt{timeline\_suc\_exp.do}
\end{figure}

@@
